taxize: taxonomic search and retrieval in R

### 2013-10-01 f1000_rev/taxize_appC.tex

Development versions of taxize are available at Github at this linke \url{https://github.com/ropensci/taxize_}, where the codebase is actively developed. This is also a good place to report bugs, submit feature requests, etc. on the Issues page \url{https://github.com/ropensci/taxize_/issues?state=open}.

The process of installing is a little bit more involved than from CRAN, but still quite easy using the package devtools \url{http://cran.r-project.org/web/packages/devtools/index.html}. You need to install development tools if you haven't already:

\begin{itemize}
  \item On Windows, download and install Rtools: http://cran.r-project.org/bin/windows/Rtools/. This is not an R package.
  \item On Mac, make sure you have either XCode (free, available in the app store) or the "Command Line Tools for Xcode" (needs a free apple id, available from http://developer.apple.com/downloads)
  \item On Linux, make sure you've installed not only R, but the R development devtools. This a linux package called something like r-base-dev.
\end{itemize}

>>>>

Development versions of taxize are available at Github at this link \url{https://github.com/ropensci/taxize_}, where the codebase is actively developed. This is also a good place to report bugs, submit feature requests, etc. on the Issues page \url{https://github.com/ropensci/taxize_/issues}.

The process of installing is a little bit more involved than from CRAN, but still quite easy using the package devtools \url{http://cran.r-project.org/web/packages/devtools/index.html}.
If you don't have it yet, you can install it from CRAN:

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{install.packages}\hlstd{(}\hlstr{"devtools"}\hlstd{)}
\end{alltt}
\end{kframe}
\end{knitrout}

You also need to install development tools if you haven't already:

\begin{itemize}
  \item On Windows, download and install Rtools: http://cran.r-project.org/bin/windows/Rtools/. This is not an R package.
  \item On Mac, make sure you have either XCode (free, available in the app store) or the "Command Line Tools for Xcode" (needs a free apple id, available from http://developer.apple.com/downloads)
\end{itemize}
